*Supplementary Material 2*

### 2022-02-19 ms/si2.Rmd
Update SI2
use modified CSV

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results = 'hide')
library(glue)
library(gluedown)
library(targets)
library(tarchetypes)
library(tidyverse)
library(assertr)
```

```{r prep-fossil-data}
# Set path to fossil data
fossils_data_path <- here::here("_targets/user/data_raw/Fossils_Ferns_mod.xlsx")

# Extract fossil categories (first row of fossil data)
fossils_categories <-
  readxl::read_excel(fossils_data_path, n_max = 1) %>%
	pivot_longer(names_to = "category", values_to = "raw_names", everything()) %>%
	mutate(
		category = str_replace_all(category, "\\.\\.\\.[0-9]+", "skip") %>%
			na_if("skip")) %>%
	fill(category) %>%
	mutate(category = str_to_title(category)) %>%
	filter(category != "Pteridophy")

# Get raw column names
fossils_raw_names <-
  readxl::read_excel(fossils_data_path, skip = 1)

# Get cleaned column names
fossils_clean_names <- fossils_raw_names %>% janitor::clean_names()

# Load fossils in wide format
fossils <-
fossils_clean_names %>%
	# Filter to only those actually used in the study
	filter(used == "X") %>%
	select(-used) %>%
	select(fossil_taxon, everything()) %>%
	# Format reference key for citing with pandoc
	mutate(
		reference = as.character(glue("@{reference}"))
	)

# Convert to long format
fossils_long <- fossils %>%
	mutate(across(everything(), as.character)) %>%
	pivot_longer(names_to = "var", values_to = "value", -fossil_taxon) %>%
	left_join(name_tbl, by = "var") %>%
	mutate(
		text = as.character(glue::glue("{raw_names}: {value}"))
	) %>%
	left_join(fossils_categories, by = "raw_names") %>%
	arrange(fossil_taxon, category, var_order)

#' Print a single category of fossil data
#'
#' @param fossil_data Fossil data in long form, filtered to a single
#' fossil
#' @param cat_select Category of data to print
#'
#' @return Character vector

@@

	# Print name of fossil as header in italics
	header <-
	fossil_select %>% 
		str_replace_all("_", " ") %>%
		md_italic() %>%
		md_heading(2)

	categories <- unique(data$category)

@@

	c(header, body, md_blank())
}
```

```{r print-fossils, results = "asis"}
unique(fossils_long$fossil_taxon) %>%
  map(~print_fossil(fossils_long, .)) %>%
	unlist() %>%
	glue::as_glue()
```

>>>>

```{r setup-rmd, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, results = 'hide')
library(glue)
library(gluedown)
library(tidyverse)
library(assertr)
```

```{r custom-funcs}
#' Print a single category of fossil data
#'
#' @param fossil_data Fossil data in long form, filtered to a single
#' fossil
#' @param cat_select Category of data to print
#'
#' @return Character vector

@@

	# Print name of fossil as header in italics
	header <-
	data %>% 
		filter(var == "fossil_taxon_header") %>%
		pull(value) %>%
		str_replace_all("_", " ") %>%
		md_italic() %>%
		md_heading(1)

	categories <- data %>%
		filter(!is.na(category)) %>%
		pull(category) %>%
		unique()

@@

	c(header, body, md_rule())
}
```

```{r prep-fossil-data}
# Set path to fossil data
fossils_data_path <- here::here("_targets/user/data_raw/Fossils_Ferns.csv")

# Extract fossil categories (first row of fossil data)
fossils_categories <-
  read_csv(fossils_data_path, n_max = 1) %>%
	pivot_longer(names_to = "category", values_to = "raw_names", everything()) %>%
	mutate(
		category = str_replace_all(category, "\\.\\.\\.[0-9]+", "skip") %>%
			na_if("skip")) %>%
	fill(category) %>%
	mutate(category = str_to_title(category)) %>%
	filter(category != "Pteridophy")

# Get raw column names
fossils_raw_names <-
  read_csv(fossils_data_path, skip = 1)

# Load data with cleaned column names
fossils_clean_names <- fossils_raw_names %>% janitor::clean_names()

# Tidy fossils in wide format
fossils <-
fossils_clean_names %>%
	# Filter to only those actually used in the study
	filter(used == "X") %>%
	select(-used) %>%
	select(fossil_taxon, everything())

# Convert to long format
fossils_long <- fossils %>%
	mutate(
		across(everything(), as.character),
		fossil_taxon_header = glue("†{fossil_taxon}")) %>%
	pivot_longer(names_to = "var", values_to = "value", -fossil_taxon) %>%
	left_join(name_tbl, by = "var") %>%
	mutate(
		text = as.character(glue::glue("{raw_names}: {value}"))
	) %>%
	left_join(fossils_categories, by = "raw_names") %>%
	arrange(fossil_taxon, category, var_order)
```

These data are exported from the FernCal v1.0 database (https://github.com/pteridophy/FossilFerns), which includes `r nrow(fossils_clean_names)` records of fossils to use as calibration points for molecular dating of ferns.

"NFos" is the unique ID of the record in FernCal.

Taxonomy of extant taxa follows pteridocat v1.0 database (https://github.com/pteridophy/pteridocat).

For a summary of these data in CSV format, see Table FIXME <add table number>.

\newpage

```{r print-fossils, include = TRUE, results = "asis", eval = TRUE}
unique(fossils_long$fossil_taxon) %>%
  map(~print_fossil(fossils_long, .)) %>%
	unlist() %>%
	glue::as_glue()
```

# References
